### 2014-10-09 tex/definitions.tex
re-orging

\subsection{Definitions}

In Javalite, states are strings that match a certain pattern.

\begin{definition}
\label{def:state}
The set of \textbf{states} $\mathcal{S}$ is defined as the set of strings matching the pattern $s$ in \ref{fig:machine-syntax}.
\end{definition}

\begin{definition}
\label{def:initstate}
$\mathcal{S}_0$ is defined as the set of \textbf{initial states}. An initial state is a state meeting the following conditions:  The range of L has exactly three locations: $l_{null}$, $l_{un}$, and $l_0$, the function R is defined only for location $l_0$, and for any field $f$, $R(l_0,f)$ returns $r_{un}$. 
\end{definition}

You can think references as a pointers to sets of locations. More concretely, a reference is an integer that the $R$ function maps to a set of constraint, location pairs that define where it points to. Within a machine state, references are string encodings of integers.

\begin{definition}
The set of \textbf{references} $\mathcal{R}$ is defined as the set of natural numbers
 $$\mathcal{R} = \mathbb{N}$$
\end{definition}

In order to make the distinction between different types of references, we partition the set of references using modular arithmetic. Stack references are those references which are created as a result of a field read. The total number of references in a representing state and a represented state are generally not the same. However, the number of references on the stack in either state is always the same.

\begin{definition}
The set of \textbf{stack references} $\mathcal{R}_t$ is defined as
 $$\mathcal{R}_t =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 0\}$$. 
\end{definition}

Input heap references are references that exist prior to program execution in the symbolic input heap. While this set of references may be infinite, they are discovered one at a time via lazy initialization.

\begin{definition}
The set of \textbf{input heap references} $\mathcal{R}_h$ is defined as
 $$\mathcal{R}_h =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 1\}$$. 
\end{definition}

\begin{definition}
The set of \textbf{new heap references} $\mathcal{R}_f$ is defined as
 $$\mathcal{R}_n =\{i \in \mathbb{N} \mid ( i\ \bmod\ 3 ) = 2\}$$. 
\end{definition}

\begin{definition}
For a given function $f:A \mapsto B$, the \textbf{image} $f^\rightarrow$ and \textbf{preimage} $f^\leftarrow$ are defined as
\begin{align}
 f^\rightarrow &= \{ f(a) \mid a \in A\}\\
 f^\leftarrow &= \{ a \mid f(a) \in B \}
 \end{align}
 The bracket notation $ f^\rightarrow [C] $ is used to denote that the image is drawn from a specific subset:
 \begin{align}
 f^\rightarrow [C] &= \{ f(a) \mid a \in C\}\\
 f^\leftarrow [D] &= \{ a \mid f(a) \in D \}
 \end{align}
 Where $C \subset A$ and $D \subset B$
\end{definition}

\begin{definition}
A \textbf{state transition relation} $\rightarrow_{\Phi}$ is a binary relation $\rightarrow_{\Phi}\ \subseteq\ \mathcal{S} \times \mathcal{S} $, which relates machine states with successor states. Two important state transition relations are \textbf{GSE} $\rgse$ and \textbf{symbolic} $\rsym$. Each of these use a separate relation for initialization: $\rinit$ for GSE and $\rsum$ for symbolic. All of these transition relations are defined in \figref{fig:lazy}, \figref{fig:lazyInit}, \figref{fig:sym}, and \figref{fig:symInit}.
\end{definition}

>>>>

\subsection{Heap Properties}

### 2014-10-09 tex/javalite.tex
re-orging

\section{Javalite}
\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is the
machine syntax. Javalite is syntactic machine defined as rewrites on a
string. The semantics use a CEKS model with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (K)ontinuation for what is to be executed next, and
a (S)tore for the heap.

\input{surface-syntax}
\input{machine-syntax}

The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
value $\cfgnt{v}$. The value can be a reference, $\cfgnt{r}$ or one of
the special values $\cfgt{null}$, $\cfgt{true}$, or
$\cfgt{false}$. Although the Javalite machine is purely syntactic, for
clarity and brevity in the presentation, the more complex structures
such as the environment are treated as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
in the environment. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

The heap is a labeled bipartite graph consisting of references,
$\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine syntax in
\figref{fig:machine-syntax} defines that graph in $\cfgnt{L}$, the
location map, and $\cfgnt{R}$, the reference map. As done with the
environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
of location-constraint pairs in the heap associated with the given
reference, and$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap.

As the updates to $\cfgnt{L}$ and $\cfgnt{R}$ are complex in the
machine semantics, predicate calculus is used to describe updates to
the functions. Consider the following example where $\cfgnt{l}$ is
some location and$\rho$ is a set of references.
\[
\cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}][\forall \cfgnt{r}^\prime \in \rho\ \lp \cfgnt{r}^\prime \mapsto \lp \cfgt{true}\ l_\mathit{null}\rp \rp ]
\]
The new partial function $\cfgnt{L}^\prime$ is just like $\cfgnt{L}$ only it
remaps $\cfgnt{r}$, and it remaps all the references in $\rho$.

The location $\cfgnt{l}_\mathit{null}$ is a special location in the heap
to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) = \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$

The initial state of the machine needs to be defined.

\input{javalite-common}

The rewrite rules that define the Javalite semantics are in
\figref{fig:javalite-common}.

>>>>

\section{Preliminaries}

\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. \figref{fig:machine-syntax} is the
machine syntax. Javalite is syntactic machine defined as rewrites on a
string. The semantics use a CEKS model with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (K)ontinuation for what is to be executed next, and
a (S)tore for the heap.

\input{surface-syntax}

\subsection{Environment}
The environment, $\eta$, associates a variable $\cfgnt{x}$ with a
value $\cfgnt{v}$. The value can be a reference, $\cfgnt{r}$ or one of
the special values $\cfgt{null}$, $\cfgt{true}$, or
$\cfgt{false}$. Although the Javalite machine is purely syntactic, for
clarity and brevity in the presentation, the more complex structures
such as the environment are treated as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
in the environment. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

### 2014-10-09 tex/lazy.tex
finished conditional initialization
re-orging

\begin{figure*}[t]
\begin{center}
\mprset{flushleft}
\begin{mathpar}
	\inferrule[Field Access]{
      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}\rp\\
      l \neq \cfgnt{l}_\mathit{null}\\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}\ \cfgnt{f}\rp \rightarrow^*_I 
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}\ \cfgnt{f} \rp \\\\ 
      \{\lp\phi^\prime\ l^\prime\rp\} = \cfgnt{L}^\prime\lp\cfgnt{R}^\prime\lp l,\cfgnt{f}\rp\rp \\
      \mathrm{fresh}_r\lp\rp  = \cfgnt{r}^\prime \\
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
      \lp \cfgnt{L}^\prime[\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime\ \phi_g^\prime\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
	}
\and
	\inferrule[Field Write]{
      \cfgnt{r}_x = \eta\lp \cfgnt{x}\rp\\ 
      \{\lp\phi\ l\rp\} = \cfgnt{L}\lp\cfgnt{r}_x\rp \\
      l \neq \cfgnt{l}_\mathit{null}\\\\
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \cfgnt{r}_x\ \cfgnt{f}\rp \rightarrow^*_I 
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi_g^\prime\ \cfgnt{r}_x\ \cfgnt{f} \rp \\\\ 
      \mathrm{fresh}_r\lp\rp = \cfgnt{r}^\prime\\
      \theta =  \cfgnt{L}^\prime\lp\cfgnt{r}\rp 
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp  \rightarrow \\\\
      \lp \cfgnt{L}^\prime[\cfgnt{r}^{\prime} \mapsto \theta]\ \cfgnt{R}^\prime[\lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}^\prime]\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
	}	
\and
    \inferrule[Equals (reference-true)]{
    \cfgnt{L}\lp \cfgnt{r}_0\rp = \cfgnt{L}\lp \cfgnt{r}_1\rp\\
    \phi_g^\prime = \lp\phi_g \wedge r_0 = r_1\rp
    }{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{true}\ \cfgnt{k}\rp 
    }
\and
    \inferrule[Equals (reference-false)]{
    \cfgnt{L}\lp \cfgnt{r}_0\rp \neq \cfgnt{L}\lp \cfgnt{r}_1\rp\\
    \phi_g^\prime = \lp\phi_g \wedge r_0 \neq r_1\rp
   }{
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g\ \eta\ \cfgnt{r}_0\ \lp \cfgnt{r}_1\ \cfgt{=}\ \cfgt{*} \rightarrow \cfgnt{k}\rp \rp  \rightarrow \\\\
    \lp \cfgnt{L}\ \cfgnt{R}\ \phi_g^\prime\ \eta\ \cfgt{false}\ \cfgnt{k}\rp 
    }
\end{mathpar}
\end{center}
\caption{Generalized symbolic execution with lazy initialization.}
\label{fig:lazy}
\end{figure*}

>>>>

\section{Initialization of Symbolic References}

In this section we present the Javalite rewrite rules for the concrete
as well as summary initialization of symbolic references. The
initialization rules are defined on the bi-partite graph consisting of
references and locations. The lazy initialization of symbolic
references consists of three key points of non-determinism where each
symbolic reference can be initialized non-deterministically to null, a
new instance of the symbolic reference, or aliases to symbolic
references of the same type previously initialized. The initialization
in GSE consists of creating branches in the execution tree for all the
non-deterministic choices. On the other hand, the heap summarization
approach creates a single branch that contains the summarization for
all the initialization in a single bi-partitate graph.

\input{initialize-lazy}
\input{summarize-precise}

The initialization rules are invoked when an uninitialized field in a
symbolic reference is accessed. The function $\mathbb{UN}(\cfgnt{L},
\cfgnt{R}, \cfgnt{r}, \cfgnt{f}) = \{\cfgnt{l}\ ...\}$ returns
constraint-location pairs in which the field $\cfgnt{f}$ is
uninitialized:
\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]
where $\mathbb{S}(\phi)$ returns true if $\phi$ is
satisfiable. Intutively, for the reference, $\cfgnt{r}$, it constructs
the set, $\theta$, that contains all contraint-location pairs that
point to the field $\cfgnt{f}$ and $\cfgnt{f}$ points to
$\cfgnt{l}_\mathit{un}$. The cardinality of the set, $\theta$ is never
greater than one in GSE and the constraint is always satisfiable
because all constraints are constant. This property is relaxed in GSE
with heap summaries.

The rules in~\figref{fig:lazyInit} present the rewrite rules for the
concrete initialization of symbolic heap objects.  These rules are
invoked until a fix pointed is reached.

The initialize (null) rewrite rule in~\figref{fig:lazyInit} first
checks that the field, $\cfgnt{r}$ is uninitialized. The fresh method
returns a new input heap reference from the partition

\section{Accessing and Writing to Field References}

\section{Equality and InEquality of References}

\input{lazy-fig}
